---
title: "LA_7"
author: "Adam Hayes, Richard Park, Jasmine Sanchez, Erin Omyer"
date: "2/26/2019"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
install.packages('data.table', repos = 'household_power_consumption.txt')
library(data.table)
data <- fread('household_power_consumption.txt',
               na.strings = c("NA", "", "?"))
```



###Adam's Findings

####How does the time of day affect the energy output of an electric water heater and air conditioner?
This is intriguing because many people may not be aware of when(during the day) their water heater and air conditioner are consuming the most energy.  It's easy to know at what times of the year you will consume the most energy with these household items, but knowing which times of the day they consume the most, regardless of time of year, can help people reduce their use much more efficiently in the longrun.

```{r}
water_and_air <- data %>%
  filter(Sub_metering_3 > 0)%>%
  count()
time_of_day <- data%>%
  filter(Sub_metering_3 > 0, Time < 12:00:00)%>%
  count()
```
```{r echo = FALSE, results = 'asis'}
library(knitr)
kable(time_of_day / water_and_air, caption = "Prob that time of day is AM, given that water heater/air conditioner have at least 1 watt-hour of active energy")

```


```{r}

water_and_airGRAPH1 <- data%>%
  filter(Sub_metering_3 >= 10)

ggplot(data = water_and_airGRAPH1)+
  geom_bar(mapping = aes(x = Time))+
  labs(title = "At Least 10 Watt-Hour Active Energy")
  
water_and_airGRAPH2 <- data%>%
  filter(Sub_metering_3 >= 20)

ggplot(data = water_and_airGRAPH2)+
  geom_bar(mapping = aes(x = Time))+
  labs(title = "At Least 20 Watt-Hours Active Energy")
  
```

####How I came about this:
Doing some exploratory data analysis on the time of day, and what values were higher between the sub_metering variables(1,2,and 3) I found that sub_metering_3 had the most values above 0.  Using the count function I compared the 3.  I also filtered all 3 values from highest watt-hour to lowest, and found even though sub_metering_2(laundry room) had some very high values, they were much less consistent than sub_metering_3(water heater/air conditioner).  Then I began filtering out the 0 values for sub_metering_3, and also filtering the times of day.  I explored the number of sub_metering_values of at least 1, that occurred in the morning(before 12:00:00) compared to the evening(after 12:00:00), and found that a much higher number of water heaters/air conditioners with positive watt-hour active energy occurred in the morning.

###Richard's Findings 

###How does time affect the global reactive power
This probability was surprising/intriguing because a lot of people might not realize that they consume the greatest amount of power in the mornings. It was expected that power would surge in the afternoon because people get off work and come home to engage in leisure activities (such as television) which would require more power, however, that is not the case because there's a higher probability for someone to use more power in the morning. This information can be used to help people efficiently consume power.

```{r}
Global_reactive_power <- data %>%
  filter(Global_reactive_power > 0, Time < 12:00:00)%>%
  count()
Greater_global_reactive_power <- data%>%
  filter(Global_reactive_power > 0, Time >= 12:00:00)%>%
  count()
```

```{r echo = FALSE, results = 'asis'}
library(knitr)
kable(Greater_global_reactive_power / Global_reactive_power , caption = "Prob that Global Reactive Power is above 0, given that the time is noon or later")
```

```{r}

Global_reactive_powerGRAPH1 <- data%>%
  filter(Global_reactive_power == 0)

ggplot(data = Global_reactive_powerGRAPH1)+
  geom_bar(mapping = aes(x = Time))+
  labs(title = "0 Watt-Hour reactive power globally")
  
Global_reactive_powerGRAPH2 <- data%>%
  filter(Global_reactive_power > 0)

ggplot(data = Global_reactive_powerGRAPH2)+
  geom_bar(mapping = aes(x = Time))+
  labs(title = "Greater than 0 Watt-Hours reactive power globally")
  
```

###How I came to this finding:
Doing some exploratory data analysis with regards to the time of day, and determining which values were higher in the Global Reactive Power, I found that there were a decent amount of values above 0. Therefore, I utilized the count function to compared the values. I accomplished this by filtering the values which were higher than 0 based on time. I decided that the right cut off time would be noon or 12:00:00 because that's the transition period from the morning into the afternoon so I filtered the values above 0 watts per hour based on the time cut off. I ended up discovering that there is a greater percentage of global reactive power being consumed in the morning versus the afternoon.

###Erin's Findings

####How does the increase in the years impact the energy output for the laundry room?
This is intriguing to analyze because you would think that as technology gets better that more people would be having more energy output. In specific, you would think more people would be using energy in their laundry rooms. But, as well, technology for laundry machines have become more energy efficient, and the data shows this. 
```{r}
AmountofLaundry_energy <- data %>%
  filter(Sub_metering_2 >= 0) %>%
  count()
years_Laundry <- data %>% 
  filter(Sub_metering_2 > 0, Date >= 07/01/2008) %>% 
  count()

```
```{r echo = FALSE, results = 'asis'}
library(knitr)
kable(years_Laundry / AmountofLaundry_energy, caption = "Probability of amoung of energy output for laundry from beyond 2008")

```
```{r}
AmountofLaundry_GRAPH1 <- data %>%
  filter(Sub_metering_2 == 0) 
ggplot(data = AmountofLaundry_GRAPH1) +
  geom_bar(mapping = aes(x = Date)) +
  labs(title = "0 Watts-Hour Active Energy")

AmountofLaundry_GRAPH2 <-data %>%
  filter(Sub_metering_2 > 0)
ggplot(data = AmountofLaundry_GRAPH2) +
  geom_bar(mapping = aes(x = Date)) + 
  labs(title = "Greater than 0 Watt-Hours Active Energy")
  
```

###How I came to this finding:
Doing some analysis with the amount of active energy used for laundry, I would assume that as the date increases then more laundry energy would be used. From the graphs, as the years in the study increase, the amount of energy output from laundry outputs gradually increases. As well, the amount of people that use no energy in their laundry rooms has gone down over time roughly. 



###Jasmine's Findings 

####How does kitchen appliance energy fluctate over time and how does that usage relate to the global active vs reactive power supply?
I took some time to analyze how much of the energy usage of kitchen appliances were using active power vs reactive power. Global active power represents the amount of power actually being utilized to power the appliances like microwaves, dishwashers and other non- gas powered equipment from the Sub_metering_1 values.Reactive power, however, represents useless power and I found that there is a stronger density in the later hours of the day where the Global active power greater than 500 watts is higher than reactive power. This makes sense, as households are typically so much more mobile and in a hurry during the earlier hours of the day becuase they have places to be. In the later hours of the day, households are able to settle down, and they utilize these spaces more in the evening times because it more conevenient and less time sensative. 

```{r}
Kitchen_active <- data%>%
  filter(Sub_metering_1 > 0, Global_active_power > 0.5)%>%
  count()
times_of_day <- data%>%
  filter(Sub_metering_1 > 0, Time < 12:00:00)%>%
  count() 


```

```{r echo = FALSE, results = 'asis'}
library(knitr)
kable(Kitchen_active / times_of_day, caption = "Prob that time of day is toward end of day, with the active kitchen power being greater than 500 watts")
```

```{r}
ggplot(data = data)+
  geom_point(mapping = aes(x = Time, y = Sub_metering_1 , color = Global_active_power), position = "jitter", na.rm = TRUE)+
  labs(title = "Active Kitchen Energy Count")
```


####How I came about this finding: 
After some analyzing with the amount of active energy used in households with kitchen appliances, I hypothesize that as the time of day gets later, then more active kitchen energy would be utilized and outputted by the household. From the graphs, again, as the time of day gets later, the amount of energy output from kitch appliances arguably increases drastically. Also, there is a higher amount of people who are using these appliances in later parts of the day as described above due to households being more mobile and productive during morning hours that these are not used as often during these hours, which increases the amount of reactive power being used. 